$Z^\prime$ mass limits and the naturalness of supersymmetry

### 2015-03-04 paper/e6ssm-tuning-paper.tex
Fixed typo m_{qi} instead of m_{Qi}
Added two-loop beta for m_S^2

\beta_{m_S^2}^{(2)}&=,\label{eq:USSMms2BetaTwoLoop}\\

@@

&{}+\frac{64}{45}g_3^2g_1^2\left [ 8\left (M_1^2+M_1M_3+M_3^2\right )-3\sum_{i=1}^3\left ( m_{di}^2-m_{Di}^2+m_{\overline{D}i}^2+m_{qi}^2-2m_{ui}^2\right )\right ]\nonumber\\

>>>>

\beta_{m_S^2}^{(2)}&=\sum_{i=1}^3\bigg [ -16\lambda_i^2\left ( m_{H_i^u}^2+m_{H_i^d}^2+m_S^2 \right )-24\kappa_i^2\left ( m_{Di}^2+m_{\overline{D}i}^2+m_S^2 \right )\nonumber\\
&{}-32\lambda_i^2a_{\lambda_i}^2-48\kappa_i^2a_{\kappa_i}^2\bigg ]-12\lambda^2y_t^2\left ( 2m_{H_u}^2+m_{H_d}^2+m_S^2+m_{Q3}^2+m_{u3}^2\right )\nonumber\\
&{}-12\lambda^2y_b^2\left ( m_{H_u}^2+2m_{H_d}^2+m_S^2+m_{Q3}^2+m_{d3}^2\right )\nonumber\\
&{}-4\lambda^2y_\tau^2\left ( m_{H_u}^2+2m_{H_d}^2+m_S^2+m_{L3}^2+m_{e3}^2\right )-12\left ( \lambda a_t+y_ta_\lambda\right )^2-12\left ( \lambda a_b+y_ba_\lambda\right )^2\nonumber\\
&{}-4\left ( \lambda a_\tau+y_\tau a_\lambda\right )^2+32g_3^2\sum_{i=1}^3\left [ \kappa_i^2\left ( m_S^2+m_{Di}^2+m_{\overline{D}i}^2+2M_3^2\right )+a_{\kappa_i}^2-2\kappa_ia_{\kappa_i}M_3 \right ]\nonumber\\
&{}+12g_2^2\sum_{i=1}^3\left [ \lambda_i^2\left ( m_{H_i^d}^2+m_{H_i^u}^2+m_S^2+2M_2^2\right )+a_{\lambda_i}^2-2\lambda_ia_{\lambda_i}M_2\right ]\nonumber\\
&{}+\frac{4}{5}g_1^2\sum_{i=1}^3\bigg [ 3\lambda_i^2\left ( m_{H_i^d}^2+m_{H_i^u}^2+m_S^2+2M_1^2\right )+2\kappa_i^2\left ( m_S^2+m_{Di}^2+m_{\overline{D}i}^2+2M_1^2\right )\nonumber\\
&{}+3\left (a_{\lambda_i}^2-2\lambda_ia_{\lambda_i}M_1\right )+2\left (a_{\kappa_i}^2-2\kappa_ia_{\kappa_i}M_1\right )\bigg ]\nonumber\\
&{}+4g_1'^2\sum_{i=1}^3\bigg [ 2\lambda_i^2\left ( Q_1^2+Q_2^2-Q_S^2\right )\left ( m_{H_i^d}^2+m_{H_i^u}^2+m_S^2+2M_1'^2\right )\nonumber\\
&{}-2Q_S\lambda_i^2\left ( Q_1m_{H_i^d}^2+Q_2m_{H_i^u}^2+Q_Sm_S^2\right )+3\kappa_i^2\left ( Q_D^2+Q_{\overline{D}}^2-Q_S^2\right )\times\nonumber\\
&{}\times\left ( m_S^2+m_{Di}^2+m_{\overline{D}i}^2+2M_1'^2\right )-3Q_S\kappa_i^2\left ( Q_Sm_S^2+m_{Di}^2+m_{\overline{D}i}^2\right )\nonumber\\
&{}+2\left ( a_{\lambda_i}^2-2\lambda_ia_{\lambda_i}M_1'\right )\left ( Q_1^2+Q_2^2-Q_S^2\right )+3\left ( a_{\kappa_i}^2-2\kappa_ia_{\kappa_i}M_1'\right )\left ( Q_D^2+Q_{\overline{D}}^2-Q_S^2\right )\bigg ]\nonumber\\
&{}-24Q_Sg_1'^2y_t^2\left ( Q_2m_{H_u}^2+Q_Qm_{Q3}^2+Q_um_{u3}^2\right )-24Q_Sg_1'^2y_b^2\left ( Q_1m_{H_d}^2+Q_Qm_{Q3}^2+Q_dm_{d3}^2\right )\nonumber\\
&{}-8Q_Sg_1'^2y_\tau^2\left ( Q_1m_{H_d}^2+Q_Lm_{L3}^2+Q_em_{e3}^2\right )+32Q_Sg_3^2g_1'^2\sum_{i=1}^3\big ( 2Q_Qm_{Qi}^2+Q_um_{ui}^2\nonumber\\
&{}+Q_dm_{di}^2+Q_Dm_{Di}^2+Q_{\overline{D}}m_{\overline{D}i}^2\big )+12Q_Sg_2^2g_1'^2\bigg [ Q_{\overline{H'}}m_{\overline{H'}}^2+Q_{H'}m_{H'}^2\nonumber\\
&{}+\sum_{i=1}^3\left ( 3Q_Qm_{Qi}^2+Q_Lm_{Li}^2+Q_1m_{H_i^d}^2+Q_2m_{H_i^u}^2\right )\bigg ]+\frac{4}{5}Q_Sg_1^2g_1'^2\bigg [ 3Q_{\overline{H'}}m_{\overline{H'}}^2+3Q_{H'}m_{H'}^2\nonumber\\
&{}+\sum_{i=1}^3\big ( 2Q_dm_{di}^2+2Q_{\overline{D}}m_{\overline{D}i}^2+2Q_Dm_{Di}^2+6Q_em_{ei}^2+3Q_1m_{H_i^d}^2+3Q_2m_{H_i^u}^2+3Q_Lm_{Li}^2\nonumber\\
&{}+Q_Qm_{Qi}^2+8Q_um_{ui}^2\big )\bigg ]+8Q_Sg_1'^4\bigg [ 3Q_SM_1'^2\big ( 9Q_d^2+9Q_{\overline{D}}^2+9Q_D^2+3Q_e^2+6Q_1^2+6Q_2^2\nonumber\\
&{}+2Q_{\overline{H'}}^2+2Q_{H'}^2+6Q_L^2+18Q_Q^2+5Q_S^2+9Q_u^2\big )+2Q_{\overline{H'}}^3m_{\overline{H'}}^2+2Q_{H'}^3m_{H'}^2\nonumber\\
&{}+6Q_Q^3m_{Qi}^2+Q_S^3m_{Si}^2+3Q_u^3m_{ui}^2\big )+2Q_SQ_{\overline{H'}}^2m_{\overline{H'}}^2+2Q_SQ_{H'}m_{H'}^2\nonumber\\
&{}+Q_S\sum_{i=1}^3\big ( 3Q_d^2m_{di}^2+3Q_{\overline{D}}^2m_{\overline{D}i}^2+3Q_D^2m_{Di}^2+Q_e^2m_{ei}^2+2Q_1^2m_{H_i^d}^2+2Q_2^2m_{H_i^u}^2+2Q_L^2m_{Li}^2\nonumber\\
&{}+6Q_Q^2m_{Qi}^2+Q_S^2m_{Si}^2+3Q_u^2m_{ui}^2\big )\bigg ],\label{eq:USSMms2BetaTwoLoop}\\

@@

&{}+\frac{64}{45}g_3^2g_1^2\left [ 8\left (M_1^2+M_1M_3+M_3^2\right )-3\sum_{i=1}^3\left ( m_{di}^2-m_{Di}^2+m_{\overline{D}i}^2+m_{Qi}^2-2m_{ui}^2\right )\right ]\nonumber\\
